Compiling refinement types to dependent types

### 2020-07-11 tex/paper.tex
Better wording for the \top notation

We introduce a shorthand notation $\top$ denoting a tautologically true \emph{proposition},
used for trivial refinements that do not carry any extra information.
One good way to define $\top$ is to state the equality of the sole inhabitant of $\Unit$ to itself:
$\top \triangleq \unit = \unit$.

>>>>

We introduce a shorthand notation $\top$ denoting some tautology
which we use for trivial refinements that do not carry any extra information.
In particular, one good way to define $\top$ is
to state the equality of the sole inhabitant of $\Unit$ to itself:
$\top \triangleq \unit = \unit$.
